Supplementary Materials

### 2021-01-21 analysis/analysis.Rmd
unscaled variables

my_models$eeg <- brm(
  data = comp_summary$eeg, 
  scale(mean_value) ~ index)

@@

my_models$disp <- brm(
  data = comp_summary$threshold, 
  scale(mean_value) ~ index)

@@

```{r, fig.cap = "The effect of index and normality on log(rms) and log(ms)."}
comp_summary$eeg %>%
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$eeg, n = 100) %>%
  mutate(model = "primary eeg") -> d_plt_eeg
# 
comp_summary$threshold %>% 
   modelr::data_grid(index, normal) %>%
   add_fitted_draws(my_models$disp, n = 100) %>%
   mutate(model = "psychophysical threshold") -> d_plt_disp

@@

 bind_rows(d_plt_eeg, d_plt_disp) %>%
   ggplot(aes(x =  index, y = .value, color = as.factor(normal), group = interaction(.draw, normal))) +
   geom_line(alpha = .15) +
   facet_wrap(~ model, scales="free_y") + 
   geom_jitter(
     data = d_summary, 
     aes(x =  index, y = mean_value, colour = as.factor(normal), group = 1), width = 0.1, height = 0, alpha = 0.33) +
   theme_minimal() + 
   ggthemes::scale_colour_ptol(labels = c("non-normal", "normal")) + 
   scale_x_continuous("index", breaks = c(2,3,4,6,8,12)) +
   scale_y_continuous("value") +
   theme(panel.grid.minor = element_blank(), legend.title = element_blank()) 
```

>>>>

my_models$eeg <- brm(
  data = comp_summary$eeg, 
  mean_value ~ index)

@@

my_models$disp <- brm(
  data = comp_summary$threshold, 
  mean_value ~ index)

@@

```{r, fig.cap = "The effect of index on log(rms) and log(ms)."}
comp_summary$eeg %>%
  modelr::data_grid(index, normal) %>%
  add_fitted_draws(my_models$eeg, n = 100) %>%
  mutate(model = "primary eeg") -> d_plt_eeg
# 
comp_summary$threshold %>% 
   modelr::data_grid(index, normal) %>%
   add_fitted_draws(my_models$disp, n = 100) %>%
   mutate(model = "psychophysical threshold") -> d_plt_disp

@@

 bind_rows(d_plt_eeg, d_plt_disp) %>%
   ggplot(aes(x =  index, y = .value, group = interaction(.draw, normal))) +
   geom_line(alpha = .15) +
   facet_wrap(~ model, scales="free_y") + 
   geom_jitter(
     data = d_summary, 
     aes(x =  index, y = mean_value, group = 1), width = 0.1, height = 0, alpha = 0.33) +
   theme_minimal() + 
   ggthemes::scale_colour_ptol(labels = c("non-normal", "normal")) + 
   scale_x_continuous("index", breaks = c(2,3,4,6,8,12)) +
   scale_y_continuous("value") +
   theme(panel.grid.minor = element_blank(), legend.title = element_blank()) 
```
